---
title: "COVID Modeling and the Crop Cycle"
author: "Prepared May/June 2020 by the Data, Monitoring, and Analytics Team at USAID/RFS"
date: "`r format(Sys.time(), '%d %B, %Y, %H:%M:%S %Z')`"
output:
  # pdf_document:
  #   toc: true
  #   toc_depth: 3
  #   highlight: tango
  #   latex_engine: xelatex
  #   keep_tex: true
  html_document:
    toc: true
    toc_float: true
    toc_depth: 2
    #number_sections: true
    theme: cosmo
    highlight: tango
# header-includes:
#   - \usepackage{fontspec}
#fontsize: 10pt
#geometry: margin= 0.75in
# https://github.com/Homebrew/homebrew-cask-fonts/tree/master/Casks
#mainfont: Latin Modern Sans #Arial #Helvetica
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
source('functions.R')
suppressPackageStartupMessages(source('load_libs.R'))
# get data files we need
datadir = "~/paultangerusda drive/2020_Sync/COVID analysis (Paul Tanger)/data/"
#map.plots = readRDS(paste0(datadir, "map.plots_20200611_1057.RDS"))
# cleaner version
map.plots = readRDS(paste0(datadir, "country_plots_for_markdown_20200612_1023.RDS"))
map.plots.regions = readRDS(paste0(datadir, "plots_by_region_20200612_1125.RDS"))
PeaksbyCountry.wide.plots = read.csv(paste0(datadir, "PeaksbyCountry.wide.plots_20200611_1003.csv"))
colnames(PeaksbyCountry.wide.plots) = c("USAID_Country", "Region", "Scenario", "Peak Cases Date", "Peak Deaths Date")
```

# Overview
## Introduction
The effects of COVID-19 go well beyond the initial acute health impacts into prolonged secondary repercussions on the economy, employment, poverty levels, safe water access, food security status, crop production, and much more.  In this analysis, we looked at whether projections of COVID-19 case totals in low-and-middle-income countries (LMICs) overlapped with key phases in the crop production cycle to understand where, when, and on which important crops COVID-19 could take a toll.  From this work, we can better inform our thinking on where to focus our programming, estimate which areas will be hit hardest next, and whether COVID-19 impacts will affect crops that are significant food sources, income generators, or both.  Combined with data on the demographics of value chain actors involved in each affected crop, we could also see whether the impacts are projected to disproportionately impact women, smallholder farmers, small businesses, and other already-marginalized groups. 

## Methodology
We began with time series projections of COVID-19 case totals from a model developed by the Centre for the Mathematical Modelling of Infectious Diseases (CMMID) at the London School of Hygiene & Tropical Medicine (LSHTM)^[Data source for Model projections of COVID-19 cases and deaths over time:  Centre for the Mathematical Modelling of Infectious Diseases (CMMID) at the London School of Hygiene & Tropical Medicine (LSHTM); https://cmmid.github.io/topics/covid19/LMIC-projection-reports.html], and overlaid those data with the calendar/timing of phases of the crop cycles in various countries from the Crop Monitor initiative of the Group on Earth Observations Global Agricultural Monitoring Initiative (GEOGLAM)^[Data source for Crop calendars:  Crop Monitor initiative from Group on Earth Observations Global Agricultural Monitoring Initiative (GEOGLAM); https://cropmonitor.org/index.php/eodatatools/baseline-data/] to observe if peaks in the number of cases for a country were projected to occur at the same time as a key phase in the cycle of production for crops important to that country.

## The LSHTM model
* This model provides simulation-based estimates for COVID-19 epidemic scenarios in many low-and-middle-income countries.  The model starts with the date a country reached 50 cases (i.e. “Day 0”), and then projects the totals of several variables (cases, deaths, hospitalizations, etc.) each day over time for an ‘unmitigated’ scenario (i.e. the country takes no action to contain COVID-19 spread), as well as in six different COVID-19 containment strategies involving social distancing, shielding, or a combined approach.  The projections estimate how different containment strategies could have different outcomes on the spread and intensity of the disease in a country.  

* While you can see the full results of the LSHTM research for each country here, the line graphs in this document plot the model’s projections for each country’s case totals across time for the seven scenarios (unmitigated plus six containment strategies) for all age groups combined.  

* ‘Day 0’ is defined as the date the country reached 50 confirmed cases, according to the Johns Hopkins Coronavirus Resource Center^[Data source for Date of the 50th confirmed COVID-19 case:  Johns Hopkins University Coronavirus Resource Center; https://coronavirus.jhu.edu/].  Note that the date of 50 confirmed cases likely occurs after the date a country actually had 50 cases.  Since the model is based on the latter, this means the true peaks of the different scenarios are likely to occur earlier in time than shown here, i.e. the peaks would shift to the left.  A future update of this analysis will incorporate a more accurate estimate of the true ‘Day 0’.

* Refer to the LSHTM link in the footnotes for more details on the model, including the definition of the different scenarios, their methodologies for determining transmission rates, etc.

## The GEOGLAM crop calendars
* For each country, the timing of crop production phases was plotted for significant staple crops, and for each sub-national area where production occurs in a country.  In the case of multiple crop seasons such as maize 1 and maize 2, the more significant season in terms of total production will be labeled as the first crop, e.g, maize 1.

* The phases of the crop production cycle reflected in this analysis were defined as:

  + Planting: Start of Planting through the Early Vegetative stage
  + Idle (represents the dormancy stage of winter wheat where applicable)
  + Vegetative: Start of Vegetative period through the Reproductive period (Period of peak weeding)
  + Harvest: Ripening through Harvest

* For the crop calendars displayed in this document, each sub-national area is represented where the timing of the crop production cycle differs.  In cases where crop cycles followed the same timing throughout the country, only one crop calendar is shown for that country.


# Country Specific Information {.tabset .tabset-fade}

```{r run_loop, echo=FALSE}
# options for results are asis - passthrough.. hold - put all results below code
# maybe try this? ## {.unlisted .unnumbered}
# METHOD 3
out = NULL
for(i in seq(map.plots)){
  # METHOD 3
  out = c(out, knit_expand('CountryTemplate.Rmd')) # this is for child template option
}
# `r paste(knit(text = out), collapse = '\n')`

out2 = NULL
# maybe move this inside the other loop - not sure how we want to display regions
for(i in seq(map.plots.regions)){
  for(j in seq(map.plots.regions[[i]]$crop_plots)){
    out2 = c(out2, knit_expand('CountryRegionTemplate.Rmd')) # this is for child template option
  }
}

```

`r paste(knit(text = out), collapse = '\n')`
`r paste(knit(text = out2), collapse = '\n')`

Data sources:
Model projections of COVID-19 cases and deaths over time: Centre for the Mathematical Modelling of Infectious Diseases (CMMID) at the London School of Hygiene & Tropical Medicine (LSHTM); https://cmmid.github.io/topics/covid19/LMIC-projection-reports.html
Crop calendars: Crop Monitor initiative from Group on Earth Observations Global Agricultural Monitoring Initiative (GEOGLAM); https://cropmonitor.org/index.php/eodatatools/baseline-data/. Date of the 50th confirmed COVID-19 case: Johns Hopkins University Coronavirus Resource Center; https://coronavirus.jhu.edu/. Prepared by the Data, Monitoring, and Analytics Team at USAID/Bureau for Resilience and Food Security; https://www.usaid.gov/who-we-are/organization/bureaus/bureau-resilience-and-food-security.  For questions on this analysis, please contact RFSAnalyticsQueries@usaid.gov.