
## {{names(map.plots[i])}}

```{r country-plots-{{names(map.plots[i])}}, echo = FALSE}
  # right now, setup to use combined figs, but might want to do them separately so we can change things in them
  country = "{{names(map.plots[i])}}"
  grid.arrange(map.plots[[country]][['bottom']])
```

```{r country-table-{{names(map.plots[i])}}, results='asis', echo = FALSE}
  # little table of key dates
  # can use kable or pander
  # https://cran.r-project.org/web/packages/kableExtra/vignettes/awesome_table_in_html.html
  country = "{{names(map.plots[i])}}"

  tabledata = PeaksbyCountry.wide.plots[PeaksbyCountry.wide.plots$USAID_Country == country, ]
  print(tabledata[,c(3:5)] %>%
      kable( row.names = F, booktabs = T) %>% #caption = "Estimates of key dates",
      kable_styling(font_size=9, position = "left", bootstrap_options = c("striped", "hover", "condensed", full_width=F, position = "left"), latex_options = c("striped", "hold_position")))

```

```{r country-maps-{{names(map.plots[i])}}, results='asis', fig.width = 2.5, echo = FALSE}
  # these are the country maps

  # align them? https://stackoverflow.com/questions/32780320/consistent-figures-size-with-gridextra-in-rmarkdown-knitr-html
  # https://stackoverflow.com/questions/53659160/r-markdown-positioning-table-and-plot-side-by-side
  # plots side by side
  # https://bookdown.org/yihui/rmarkdown-cookbook/figures-side.html
  # https://sebastiansauer.github.io/two-plots-rmd/
  # https://stackoverflow.com/questions/37115276/control-alignment-of-two-side-by-side-plots-in-knitr
  country = "{{names(map.plots[i])}}"
  # the actual maps
  grid.arrange(map.plots[[country]][['map_plot']])
```

Data sources^[
Model projections of COVID-19 cases and deaths over time: Centre for the Mathematical Modelling of Infectious Diseases (CMMID) at the London School of Hygiene & Tropical Medicine (LSHTM); https://cmmid.github.io/topics/covid19/LMIC-projection-reports.html
Crop calendars: Crop Monitor initiative from Group on Earth Observations Global Agricultural Monitoring Initiative (GEOGLAM); https://cropmonitor.org/index.php/eodatatools/baseline-data/. Date of the 50th confirmed COVID-19 case: Johns Hopkins University Coronavirus Resource Center; https://coronavirus.jhu.edu/. Prepared by the Data, Monitoring, and Analytics Team at USAID/Bureau for Resilience and Food Security; https://www.usaid.gov/who-we-are/organization/bureaus/bureau-resilience-and-food-security.  For questions on this analysis, please contact RFSAnalyticsQueries@usaid.gov.]

\newpage